---
title: "Job Tracker for Randy Swaty"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: yeti
    
self_contained: true
---

```{r setup, include=FALSE}
library(flexdashboard)
library(rgdal)
library(raster)
library(htmlwidgets)
library(leaflet)
library(tidyverse)
library(sf)
```



Place-based Projects
========================================================

##  Need something here

<font size="6"> Map of spatially relevant projects. </font>


```{r read projects, message=FALSE, warning=FALSE, include=FALSE}
projects <- st_read('sData/projects.shp')

# add in components
components <- read_csv("components.csv")
#View(components)

projects <- merge(projects, components, by = 'name')
```

```{r project map, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, hide = TRUE}


# Make popup
popup <- paste("Project Name", projects$name, "<br>",
              "Sufficiency:", projects$sufficiency, "<br>",
              "Durability:", projects$durability, "<br>",
              "Condition:", projects$condition)


# da map
projectsMap <-
  leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  setView(-98.483330, 38.712046, zoom = 4) %>%  
  addPolygons(data = projects, 
              fill = TRUE, 
              fillOpacity = 0.7,
              fillColor = '#B1DAB3',
              stroke = TRUE, 
              weight = 0.5,
              color = "#526653",
              popup = ~popup)

projectsMap
```
  
<br>

**In the pop-up you will see:**

* Name-brief name of project
* Sufficiency (0-4, low to high): High means that I feel that I have the time, data, support, knowledge and/or guidance to be successful. 
* Durability (0-4, low to high): High means there is that the project leads to lasting conservation, education and/or partnerships.
* Condition (0-4, low to high): High means the project is progressing according to schedule, partnerships are in good shape (regarding quality and quantity of communication and trust) and/or the deliverables are being generated as expected. 


Column {.sidebar}
-----------------------------------------------------------------------
<b><font  size="4em" color="#000000">This map...</font></b>  

This map represents "spatially-relevant" projects I participate in, starting December, 2021.  I will be adding project boundaries as I meet people, or take on major work (i.e., I am not looking backwards to projects I have completed, or forward to possible projects).  There will be many additions over the next few months.

Also see "Non-spatial projects" tab for projects that are national, may not have a definite geography or are people-focused.  





Non-spatial projects
========================================================

## need something here for this to work

Just a clickable list.  Click to get more complete description.  Condisder a chart?

* FSC and LANDFIRE
* CDL
* etc.

Column {.sidebar}
-----------------------------------------------------------------------
<b><font  size="4em" color="#000000">What this page is for.</font></b>  

Some projects span the country (and possibly more), or are not really tied to a geography.
